LogChunks: A Data Set for Build Log Analysis

### 2020-01-31 msr-paper/paper.tex
fill in missing numbers, minor corrections, add zenodo link

\usepackage{listings}
\usepackage{tabularx}
\usepackage{cleveref}
\usepackage{xspace}
% TODO remove XD
\usepackage{xcolor}

\newcommand{\secfunc}[1]{{\color{magenta}#1}}
\newcommand{\mention}[1]{{\color{cyan}#1}}
\newcommand{\plan}[1]{{\color{purple}#1}}
\newcommand{\bp}[1]{{\color{violet}#1}}
\newcommand{\draft}[1]{{\color{blue}#1}}
\newcommand{\review}[1]{{\color{black}#1}}
\newcommand{\todo}[1]{{\color{orange}(#1)}}
\newcommand{\logchunks}{\emph{LogChunks}\xspace}

@@

\author{Carolin Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
\email{{c.e.brandt,a.panichella,a.e.zaidman,m.m.beller}@tudelft.nl}
\affiliation{
  \institution{Delft University of Technology}
  \country{The Netherlands}
}

@@

Thus, in this paper, we present \logchunks,\footnote{\logchunks
  is openly available on Zenodo: \todo{insert zenodo link}} a
collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
29 programming languages.  For each build log, we manually labeled
the chunk describing why the build failed.  The data set also provides
keywords the authors would use to search for the labeled log chunk and
categorizes the log chunks according to their format within the log.

@@

\paragraph{Log Sampling}
Travis CI builds comprise a number of jobs that actualize a build
process in different environments. Hence, the outcome from different
jobs might be different. For each build in \logchunks, we download the
first job which has the same state as the overall build.

@@

\paragraph{Search Keywords}
We presented the \texttt{Chunk} and ten lines above and below to the labeler.
Their task was to note down three strings they would put into a search field to find this failure description.
The strings should appear in or around the \texttt{Chunk} and is case-sensitive.
There are no limitations on the search string, especially spaces are allowed.

@@

We validated our collected data points in an iterative fashion. First,
we performed an initial inter-rater reliability study with a
co-author, which informed the design of a cross-validation study in
which we contacted over 200 developers.  Our learnings from the
initial internal study are that  1) it is important and difficult to
adequately communicate all decisions and assumptions on how and which data is
labeled and 2) that can be different legitimate view points on
what log chunk consitutes the cardinal error and which key words best to use.

@@

\paragraph{Method}
Using the Travis API, we collected the commit information for each build represented in \logchunks.
We grouped all commits triggered by one developer and sent out an email to them. %, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
It included links to the corresponding commits, build overview and log file.
We asked the developers to fill out a short form in case our extraction was not correct.
%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.

\paragraph{Results}
In total, from \todo{x date} to \todo{y date}, we sent out mails to 246 developers. 32 of these mails could
not be delivered. We performed the sending out in an iterative way, first with \todo{x} emails and then in a second batch the remaining \todo{y} emails, and used the first author's academic email address as thes ender. All emails were specific to each receipient, and we only sent one mail per recipient. We received answers from 61 developers, corresponding to
144 build logs (response rate: 24.8\%). When comparing this response rate with other typical response rates known from Software Engineering, it is extremely high. We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer. Indeed, we only received \todo{z} replies from developers along the lines of ``done''.

@@

\paragraph{Chunk That Describes Why The Build Failed}
The \texttt{Chunk} is the substring of the build log that describes why the build failed.
This can, for example, be the failing test case or a compiler error.
In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed, for example ``\texttt{The command "test/run !" exited with 1.}''
In \Cref{tab:data-in-example}, the \texttt{Chunk} describes a compile error where a variable did not exist in the current scope.

@@

\paragraph{Structural Category}
For each repository, we assign \emph{structural categories} to the chunks.
The structural category compares how \texttt{Chunk}s are represented within the build log.
Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
Two chunks fall into the same structural categories if they are surrounded by the same markings.
Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from \Cref{tab:data-in-example}.
In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.

\lstset{
  language=XML,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[tbp]
	\centering
\begin{lstlisting}[breaklines=true]
========DIFF========
*{\color{cyan}-=-=-=-=-=-}*
005+     Parameter #1 [<optional> $flags]
005-     Parameter #1 [<optional> $ar_flags]
========DONE========
FAIL Bug#71412 ArrayIterator reflection 
*{\color{cyan}-=-=-=-=-=-}*
TEST 9895/13942 [2/2 test workers running]
\end{lstlisting}
\vspace{-0.3cm}
	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}. \todo{We inserted the special marker} ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
	\label{lst:same-category}
\end{figure}

@@

\paragraph{Benchmarking Build Log Analysis Techniques}
\logchunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
\logchunks can be a benchmark to evaluate other build log analysis techniques.
For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.

>>>>

\usepackage{listings}
\usepackage{tabularx}
\usepackage{cleveref}
\usepackage{xspace}
\usepackage{xcolor}

\newcommand{\logchunks}{\emph{LogChunks}\xspace}

@@

\author{Carolin E. Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
\email{{c.e.brandt,a.panichella,a.e.zaidman,m.m.beller}@tudelft.nl}
\affiliation{
  \institution{Delft University of Technology}
  \country{The Netherlands}
}

@@

Thus, in this paper, we present \logchunks,\footnote{\logchunks
  is openly available on Zenodo: https://zenodo.org/record/3632351} a
collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
29 programming languages.  For each build log, we manually labeled
the chunk describing why the build failed.  The data set also provides
keywords the authors would use to search for the labeled log chunk and
categorizes the log chunks according to their format within the log.

@@

\paragraph{Log Sampling}
Travis CI builds comprise a number of jobs that actualize a build
process in different environments. Hence, the outcome from different
jobs might be different. For each build in \logchunks, we download the log of the
first job that has the same state as the overall build.

@@

\paragraph{Search Keywords}
We presented the \texttt{Chunk} and ten lines above and below to the labeler.
Their task was to note down three strings they would put into a search field to find this failure description.
The strings should appear in or around the \texttt{Chunk} and are case-sensitive.
There are no limitations on the search string, especially spaces are allowed.

@@

We validated our collected data points in an iterative fashion. First,
we performed an initial inter-rater reliability study with a
co-author, which informed the design of a cross-validation study in
which we contacted over 200 developers.  Our learnings from the
initial internal study are that  1) it is important and difficult to
adequately communicate all decisions and assumptions on how and which data is
labeled and 2) that there can be different legitimate view points on
what log chunk constitutes the cardinal error and which keywords best to use.

@@

\paragraph{Method}
Using the Travis API, we collected the commit information for each build represented in \logchunks.
We grouped all commits triggered by one developer and sent out an email to them. %, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
It included links to the corresponding commits, the build overview and the log file.
We asked the developers to fill out a short form in case our extraction was not correct.
%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.

\paragraph{Results}
In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. 32 of these mails could
not be delivered. We performed the sending out in three batches and used the first author's academic email address as the sender. All emails were specific to each recipient, and we only sent one mail per recipient. We received answers from 61 developers, corresponding to
144 build logs (response rate: 24.8\%). When comparing this response rate with other typical response rates known from Software Engineering, it is extremely high. We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer. Indeed, we only received seven replies from developers along the lines of ``done''.

@@

\paragraph{Chunk That Describes Why The Build Failed}
The \texttt{Chunk} is the substring of the build log that describes why the build failed.
This can, for example, be the failing test case or a compiler error.
In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed, for example ``\texttt{The command "test/run !" exited with 1.}''
In \Cref{tab:data-in-example}, the \texttt{Chunk} describes a failing test in which the tested process timed out.

@@

\paragraph{Structural Category}
For each repository, we assign \emph{structural categories} to the \texttt{Chunk}s.
The structural category compares how \texttt{Chunk}s are represented within the build log.
Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
Two chunks fall into the same structural categories if they are surrounded by the same markings.
Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from \Cref{tab:data-in-example}.
In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.

\lstset{
  language=XML,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[tbp]
	\centering
\begin{lstlisting}[breaklines=true]
========DIFF========
*{\color{cyan}-=-=-=-=-=-}*
005+     Parameter #1 [<optional> $flags]
005-     Parameter #1 [<optional> $ar_flags]
========DONE========
FAIL Bug#71412 ArrayIterator reflection 
*{\color{cyan}-=-=-=-=-=-}*
TEST 9895/13942 [2/2 test workers running]
\end{lstlisting}
\vspace{-0.3cm}
	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}. We inserted the special marker ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
	\label{lst:same-category}
\end{figure}

@@

\paragraph{Benchmarking Build Log Analysis Techniques}
\logchunks is a spin-off from research in which we compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
\logchunks can be a benchmark to evaluate other build log analysis techniques.
For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
